Reply To Examiners

### 2014-05-14 answer_thesis_examiner/chap3.tex
auto

\replyToComment
    {Page 133, line 3: ``it is definitely not fully representative of the data.''.
      So what kind of error it cause?
      How will it affects the use of your model?
      It is neccessary to point out what are the shortcomings and how it affects the use of your model!
    }
    {
      The thesis clearly indicated that the proposed models inherently suffer from loss of dimension where the full data is multi-dimensional and the proposed models are scalar.
}

The Examiner's next question center around this very point: ``.. definitely not full representative of the data''.
He went on to ask: ``What kind of eror will it cause?''.
To this the answer is that the model inherently suffers from loss of dimension
  where the full data is multi-dimensional and the proposed models are scalar.

Besides these main points, the chapter is updated to increase its pursuasive power.
For example: the sentence in line 1, page 133, section 6.3 is removed.
Or a list of achievements has been included in this chapter.

>>>>

\replyToComment
    {
      %Page 133, line 3: ``it is definitely not fully representative of the data.''.
      %So what kind of error it cause?
      %How will it affects the use of your model?
      It is neccessary to point out what are the shortcomings and how it affects the use of your model!
    }
    {
      The thesis clearly indicated that the proposed models inherently suffer from loss of dimension where the full data is multi-dimensional and the proposed models are scalar.
      This restrict the use of the model to a class of problem where a single scalar decision, probability, distance or number is required to represent the complex dataset.
    }

\replyToComment
    {
      A thesis is supposed to persuade others to believe what you have proposed and to use it.
      How can you expect others to believe in you, when you don't know what most of what it is supposed to do?
    }
    {
      The methodology that is employed to persuade people into believing the proposed models is to follow rigorious mathematical transformations coupled with experiments.
      The thesis also includes a chapter detailing multiple different applications of the proposed models.
      What else the proposed models can applied on, I feel, is a totally different matter.
      In the end, Eistein probably did not forsee that his theory were used to create atomic bombs and killed thousands of people!
    }

\replyToComment
    {
      On page 10, Chapter 1, the author specified a list of ``results to be obtained''.
      However, in the conclusion chapter, there is no corresponding list of achievements ...
    }
    {
      A corresponding list of achievement has been included showing that all set-out objectives are met.
    }

%The Examiner's next question center around this very point: ``.. definitely not full representative of the data''.
%He went on to ask: ``What kind of eror will it cause?''.
%To this the answer is that the model inherently suffers from loss of dimension
%  where the full data is multi-dimensional and the proposed models are scalar.
%
%Besides these main points, the chapter is updated to increase its pursuasive power.
%For example: the sentence in line 1, page 133, section 6.3 is removed.
%Or a list of achievements has been included in this chapter.
